\documentclass[11pt]{article}
\usepackage{hyperion_brand}

\begin{document}

% --- Cover Page ---
\makehyperioncover{Fit and Proper Corporate Governance Framework}{Operational Filing Outlining Board Structures, Conflict of Interest Policies, and Executive Competency Questionnaires under the VARA Company Rulebook}{004}

% --- Table of Contents ---
\newpage
\pagenumbering{roman}
\tableofcontents
\newpage

% --- Begin Body ---
\pagenumbering{arabic}
\setcounter{page}{1}

\section{Introduction and Statutory Purpose}
Corporate governance at Hyperion Realty is designed to ensure fiduciary accountability, systemic transparency, and strict alignment with regional laws. Managing tokenized real-world assets requires bridging traditional corporate governance with decentralized onchain mechanics.

This framework is prepared in compliance with the **VARA Company Rulebook** issued under the Virtual Assets and Related Activities Regulations 2023. Under these standards, all directors, senior managers, and key compliance personnel must be certified as "Fit and Proper" prior to the VASP obtaining its operational license.

\section{Board of Directors and Committee Structure}
The governing body of Hyperion Realty (Dubai VASP) is its Board of Directors. The Board operates under a formal charter, meeting at least once per calendar quarter.

\subsection{Board Composition and Independence}
The Board consists of five (5) members:
\begin{itemize}
    \item Two (2) Executive Directors: The Chief Executive Officer (CEO) and Chief Compliance Officer (CCO).
    \item One (1) Non-Executive Director representing the institutional founding partners and real estate treasury.
    \item Two (2) Independent Non-Executive Directors (INEDs) with extensive backgrounds in UAE real estate law and commercial property finance.
\end{itemize}

This composition ensures that independent oversight is integrated into all strategic board actions, preventing executive dominance and protecting the interests of token holders.

\subsection{Designated Management Committees}
To streamline operations and enforce specialized oversight, the Board establishes three permanent management committees:
\begin{enumerate}
    \item \textbf{Risk and Security Committee}: Evaluates smart contract audits, blockchain cybersecurity threats, oracle pricing feeds, and BCDR preparedness.
    \item \textbf{Sourcing and Valuation Committee}: Oversees the physical property acquisition pipeline, structural due diligence, independent appraisals, and local SPV formations.
    \item \textbf{Audit and Compliance Committee}: Supervised by an INED, this committee reviews AML monitoring metrics, internal audits, and goAML filings, and oversees relations with external regulators.
\end{enumerate}

\section{Conflict of Interest Policy}
Conflicts of interest present significant risk in real estate investment platforms. Hyperion enforces a strict, zero-tolerance policy regarding undisclosed conflicts:

\subsection{Definition of Conflict}
A conflict of interest arises when a Director, key employee, or major HPR token holder has a personal, financial, or professional interest that could compromise their objective fiduciary duty to Hyperion Realty or its property token holders. This includes:
\begin{itemize}
    \item Personal ownership or equity interest in a target property under evaluation for protocol tokenization.
    \item Holding directorships or advisory roles in competing virtual asset platforms or traditional real estate syndicates.
    \item Receiving personal commissions, rebates, or side-benefits from third-party property developers or management firms.
\end{itemize}

\subsection{Disclosure and Abstention Protocols}
\begin{regulatorybox}{Enforcement: Conflict Mitigation Workflow}
In the event that a potential conflict of interest is identified:
1. **Mandatory Registry**: The conflicted individual must immediately file a formal disclosure statement to the Audit and Compliance Committee.
2. **Abstention**: The conflicted individual is legally barred from participating in any discussions, evaluations, or votes regarding the transaction.
3. **Registry Audit**: The CCO maintains a permanent, auditable Registry of Conflict Disclosures, which is reviewed annually by external compliance auditors and made available to VARA examiners.
\end{regulatorybox}

\section{Fit and Proper Assessment Standards}
Under VARA guidelines, all individuals designated to perform controlled functions (Directors, CCO, MLRO, Head of Sourcing) must demonstrate that they satisfy the **Fit and Proper Standard**. Hyperion evaluates candidates across three primary criteria:

\subsection{Honesty, Integrity, and Reputation}
Candidates must possess an unblemished professional history. Disqualifying factors include:
\begin{itemize}
    \item Criminal convictions relating to financial crime, fraud, money laundering, or theft in any jurisdiction.
    \item Regulatory censures, suspensions, or license revocations by any financial or digital asset authority globally.
    \item Disqualification from acting as a corporate director under UAE or international company laws.
\end{itemize}

\subsection{Competence, Capability, and Experience}
Key personnel must demonstrate the technical capacity to execute their roles:
\begin{itemize}
    \item The MLRO must hold recognized compliance credentials (e.g., CAMS certification) and possess at least 5 years of experience in anti-financial crime operations.
    \item Technical leads must demonstrate deep expertise in solidity programming, EVM architectures, and secure wallet custody.
\end{itemize}

\subsection{Financial Soundness}
Candidates must demonstrate personal financial responsibility. Bankruptcy, active insolvency proceedings, or a history of severe personal debt defaults will disqualify candidates from holding fiduciary roles.

\section{Regulatory Fit and Proper Questionnaire}
Every executive officer and licensed individual at Hyperion must complete and sign this formal questionnaire during the VARA application phase:

\begin{alertbox}{Fit and Proper Candidate Disclosure Statement}
\fontfamily{phv}\selectfont\fontsize{9}{11}\selectfont
\begin{enumerate}
    \item Have you ever been convicted of any offense involving fraud, dishonesty, or financial crime in any court globally? \quad \textbf{[ YES / NO ]}
    \item Have you ever been subject to a regulatory investigation or censure by a financial regulator (such as VARA, DFSA, SEC, FCA)? \quad \textbf{[ YES / NO ]}
    \item Have you ever been dismissed from a professional position or forced to resign due to ethical or compliance breaches? \quad \textbf{[ YES / NO ]}
    \item Are you currently subject to any bankruptcy, corporate liquidation, or debt settlement proceedings? \quad \textbf{[ YES / NO ]}
    \item Do you hold any direct or indirect ownership in physical properties currently tokenized or proposed for tokenization on Hyperion? \quad \textbf{[ YES / NO ]}
\end{enumerate}
\end{alertbox}

\noindent
\textbf{Declaration}: I hereby declare that the information provided in this questionnaire is complete and accurate to the best of my knowledge. I understand that any false or misleading statement represents a severe breach of professional conduct and will result in immediate termination of my controlled function and direct referral to the Dubai Virtual Assets Regulatory Authority.

\par\vspace{1.5cm}
\noindent
\begin{tabularx}{\textwidth}{X X}
    \rule{4cm}{0.4pt} & \rule{4cm}{0.4pt} \\
    \textbf{Candidate Signature} & \textbf{Date} \\
    & \\
    \rule{4cm}{0.4pt} & \rule{4cm}{0.4pt} \\
    \textbf{Attested by Chief Compliance Officer} & \textbf{Date}
\end{tabularx}

\makehyperionseal

\end{document}
